---
title: "Report title"
subtitle: "Subtitle that indicates findings"
author: "Report prepared for MINGAR by [consulting company name]"
date: 2022-04-07
lang: "en"
output:
  pdf_document:
    template: report.tex
    toc: true
    toc_depth: 2
titlepage: true
titlepage-color: "98D7F6"
titlepage-text-color: "FFFFFF"
titlepage-rule-color: "FFFFFF"
titlepage-rule-height: 2
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE, message = FALSE, warning = FALSE)
```

# General comments (you can delete this section)

_Before making any changes, knit this Rmd to PDF and change the name of the PDf to something like 'original-instructions.pdf', or whatever you like (it is just for your reference).. Then you can delete this section and if you want to check what it said, just open the other PDF. You don't HAVE to use this particular template, but you DO need to write you report in RMarkdown and include a cover page._

_The cover page must be a single stand alone page and have:_

*	_A title and subtitle (that indicate your findings)_
* _"Report prepared for MINGAR by" your company name_
*	_Date (assessment submission date is fine)_

_You can change the colour of this cover to any colour you would like by replacing 6C3082 in the YAML above (`titlepage-color:`) to another hex code. You could use this tool to help you:_ https://htmlcolorcodes.com/color-picker/

_Note: There should NOT be a table of contents on the cover page. It should look like a cover._

\newpage
# Executive summary

_Guidelines for the executive summary:_

* _No more than two pages_
* _Language is appropriate for a non-technical audience_
* _Bullet points are used where appropriate_
*	_A small number of key visualizations and/or tables are included_
*	_All research questions are addressed_


_The [module 4 writing prompt](https://sta303-bolton.github.io/sta303-w22-courseguide/knowledge-basket-writing-and-peer-feedback.html#module-4-writing-task) provides some tips and information about writing executive summaries._


\newpage
# Technical report
_This part of the report is much more comprehensive than the executive summary. The audience is statistics/data-minded people, but you should NOT include code or unformatted R output here._


## Introduction

_Provide a brief introduction to your report and outline what the report will cover. This section is valuable for setting scope and expectations. _

### Research questions
_Use bullet points to to describe the research questions you are going to address. Write in full sentences._
- What type of customers would buy the new devices which is to find the features of our target customers?
- What is the difference between the new customers and the traditional customers with respect to different products?

```{r}
library(tidyverse)
library(polite)
library(rvest)
library(readr)


#install.packages("cancensus")
library(cancensus)

#install.packages("haven")
library(haven)

#install.packages("lubridate")
library(lubridate)

library(dplyr)
library(ggplot2)
library(Rmisc)
library(ggpubr)

library(lme4)
library(lmtest)

library(mgcv)
```

### describe data 
The collected data contains some basic information about each customers. For example, the variable that describe different sex of customers provide the difference of purchase power for new customers between different sex. Also, there is the age of customers in the dataset that give the attitudes to the new product with different age groups. Moreover, the median income of household could indirectly show the economic strengths that may affect the purchase of new products. 
  
```{r}
dat = read_rds("data/customer.Rds")
```

```{r}
# customer => dat
# new_customer => is_new
```


```{r}
dat = dat %>% mutate(is_new = as.factor(ifelse(line %in% c("Active", "Advance"), 1, 0)))
```

```{r}
dat = dat %>% filter(!is.na(sex))
```


```{r, fig.height=12, fig.cap="Features of New and Traditional Customers", include=TRUE}
g1 <- dat %>% ggplot2::ggplot(aes(x=sex)) + geom_bar(color = "white", fill = "lightblue") + 
  facet_wrap(~is_new) + theme_light()+ labs(title = "Bar plot: comparison of distribution of gender between new and traditional customers")

g2 <- dat %>% ggplot2::ggplot(aes(x=age)) + geom_histogram(color = "white", fill = "lightblue") + facet_wrap(~is_new) 
+ theme_light() + labs(title = "Histogram: comparison of median income between new and traditional users", x = "Median Income")

g3 <- dat %>% ggplot2::ggplot(aes(x=hhld_median_inc)) + geom_histogram(color = "white", fill = "lightblue") + facet_wrap(~is_new) + 
  theme_light() + labs(title = "Histogram: Distribution of new and traditional customers")

g4 <- dat %>% ggplot2::ggplot(aes(x=skin)) + geom_bar(color = "white", fill = "lightblue") + facet_wrap(~is_new) + theme_light() + 
  labs(title = "Histogram: distribution of new and traditional customers")

Rmisc::multiplot(g1, g2, g3, g4, cols = 2)
```
  
  
  
```{r}
knitr::kable(dat %>% group_by(is_new) %>% dplyr::summarise(n(), mean_median_income = mean(hhld_median_inc), mean_age = mean(age), mean_population = mean(Population)))
```



```{r}

dat <- dat %>% mutate(age_18 = age - 18)
model_glmer_initial = glmer(is_new ~ age + skin + hhld_median_inc + (1|CSDuid), family = binomial, data = dat, control=glmerControl(optimizer="bobyqa",  optCtrl=list(maxfun=2e5)))
summary(model_glmer_initial)

# age = 0 now have meanings after subtracting minimum, which is 18

```
age and median_inc is significant, so we move to linear model for age and median income



```{r}
model_simplified_gam = gam(is_new~age+s(hhld_median_inc, CSDuid, bs = "re"), family = binomial, data = dat, method = "REML")
summary(model_simplified_gam)
```



```{r}
mod_lin = lm(hhld_median_inc~is_new, data = dat)
summary(mod_lin)


# 1:34:18

#mod3 = gam(hhld_median_inc~new_customer + s(CSDuid, bs = "re"), data = customer, method = "REML")
#summary(mod3)
## GAM model

# Equivalent lm 
# mod3 = lmer(Population~new_customer + (1|CSDuid), data = customer)
# summary(mod3)

#mod4 = gam(new_customer~age+s(hhld_median_inc, CSDuid, bs = "re"), family = binomial, data = customer, method = "REML")
#summary(mod4)
```

```{r}
# Load the data
cust_sleep <- read_rds("data/cust_sleep.Rds")
sleep_data <- read_rds("data/sleep_data.Rds")
```

```{r}
# calculate flag per minute sleep
sleep_data <- sleep_data %>%
  mutate(flag_per_minute = flags/duration)
```

```{r}
# Table
knitr::kable(sleep_data %>% 
  group_by(skin) %>%
  summarise(mean(flag_per_minute)), caption = "Average Flag per Minute for Users in Different Skin Colors", col.names = c("flag/minute"))
```

```{r, fig.cap="Device Performance Across Users With Different Skin Color Types", include=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
#Plot a graph showing device performance on sleep scoring across different skin color users
sleep_data %>% 
  ggplot(aes(x = flag_per_minute, fill = skin)) +
  geom_histogram()+
  scale_fill_brewer(palette = "Blues") + 
  labs(x = "Flag/minute", 
       y = "Quantity", 
       title = "Histogram that shows the device performance across users with different skin color types")
```

```{r,fig.cap="Relation Between Age and Average Flag/minute", include=TRUE, echo = FALSE, message=FALSE, warning=FALSE}
sleep_data %>% 
  ggplot(aes(x = age, y= flag_per_minute)) +
  geom_point(color = "lightblue")+
  geom_smooth(formula = y~x, method = "glm") + 
  labs(title = "Scattorplot showing the relationship between age and age flag/minute", 
       x = "Age", 
       y = "Flage/minute") 

```

$$ 
log(\frac{p}{1-p}) = \beta_0 + \beta_1*skin + (1|customer\ id)
$$

```{r}
# Fit GLM for only skin on flag with random effect caused by more than one observed data under one customer id 
mod1 <- glmer(flags ~ skin + (1|cust_id),
              offset = log(duration),
              family = poisson,
              data = sleep_data)

summary(mod1)
```



$$
log(\frac{p}{1-p}) = \beta_0 + \beta_1*skin + \beta_2*age + \beta_3*median\ income +(1|customer\ id)
$$

```{r}
# Fit GLM for skin, age and household median income on flag with random intercept effect of customer id and random slope effect of household median income 
mod2 <- glmer(flags ~ skin + age + hhld_median_inc + (1|cust_id), 
              offset = log(duration),
              family = poisson,
              data = sleep_data)

summary(mod2)
```

$$
log(\frac{p}{1-p}) = \beta_0 + \beta_1*skin + \beta_2*age +(1|customer\ id)
$$

```{r}
# Fit GLM for skin and age on flag with random intercept effect of customer id 
mod3 <- glmer(flags ~ skin + age + (1|cust_id), 
              offset = log(duration),
              family = poisson,
              data = sleep_data)

summary(mod3)
```

```{r}
# ANOVA test to compare models
anova(mod1, mod3)
```

Table: ANOVA Test Result

Parameter | AIC | BIC | P-value | 
--------- | --- | --- | ------- |
mod1 | 85563 | 85618 |          |
mod3 | 85557 | 85621 | 0.006874 |

Table: Summary of Final Model

Parameter | Estimate | Std. Error | z value | P-value |
--------- | -------- | ---------- | ------- | ------- |
Intercept | -3.383919 | 0.009345 | -362.107 | < 2e-16 |
skinDefault | -1.631511 | 0.011888 | -137.235 | < 2e-16 |
skinMedium | -1.212081 | 0.012817 | -94.566 | < 2e-16 |
skinMedium-light | -1.613651 | 0.014043 | -114.905 | < 2e-16 |
skinLight | -2.390047 | 0.017450 | -136.966 | < 2e-16 |
skinMedium-dark | -0.499462 | 0.010935 | -45.675 | < 2e-16 |
age | -0.046881 | 0.017293 | -2.711 | 0.00671 |

$$
log(\frac{p}{1-p}) = -3.383919-1.631511*skinDefault-1.212081*skinMedium-1.613651*skinMedium-
$$
$$
light-2.390047*skinLight-0.499462*skinMedium-dark-0.046881*age$$
```{r, include=FALSE}
# Calulate the confidence interval
confint(mod3)
```

Table: Results of the Confidence Interval

Parameter | 2.5% | 97.5% |
.sig01 | 0.03737178 | 0.06225316 |
Intercept | -3.40235708 | -3.36559555 |
skinDefault | -1.65486300 | -1.60819400 |
skinMedium | -1.23728740 | -1.18695944 | 
skinMedium-light | -1.64125960 | -1.58614939 |
skinLight | -2.42437851 | -2.35594678 | 
skinMedium-dark | -0.52097854 | -0.47797305 |
age | -0.08083102 | -0.01293586 |


```{r}
#filter out the portion of device performance from dark people 
customer_dark = sleep_data %>% filter(skin == "Dark")
```

```{r}
# fit a glmm of product line on the number of flags, random effect is the customer ID and the offset term is the length of the sleep time
mod4 <- glmer(flags ~ line + (1|cust_id), 
              offset = log(duration),
              family = poisson,
              data = customer_dark)
summary(mod4)
```

## Informative title for section addressing a research question

_For each research question, you will want to briefly describe any data manipulation, show some exploratory plots/summary tables, report on any methods you use (i.e. models you fit) and the conclusions you draw from these_

```{r}
# This chunk provides an example of some things you can do with RMarkdown 

# read in the data (this will only work once you've set up the data!)
#device_data <- read_csv("data-raw/device.Rds")

# create a visualization
#device_data %>% 
#  ggplot(aes(x = ))

```

## Informative title for section addressing a research question


## Discussion

According to the graph, the new customers who are females (~60%) are more than males (~40%), with small proportion for intersex customers. Furthermore, the ages of new customers spreads over different age groups with a small population over 75-year-old group and the highest target age groups are people who are around 30 years old and 60 years old based on the histogram. In addition, people who have the income around 100,000 are more likely to buy this new product, and the income of 50,000 is the second largest group but the population just has half of the 100,000 group. Additionally, the last graph shows that people of different skins have almost the same purchase power of the new product. 
The table shows a more clear data of the new customers. The average household median income of the new buyers are around 69,000. The average age of the new buyers are around 48. Also, people who live in the neighborhood with population of around 1,500,000 are more likely to buy this new product. 

Comparing between new customers and traditional customers through table and graphs:
By comparing the new customers and traditional customers through the graphs, the number of new customers becomes larger than the traditional customers, which females are still larger than males and the number of people increases for each skin groups. Also, the new product attracts more teenagers than those tradition products. Moreover, the number of people in each groups of household median income increases as well. 
By comparing the new customers and traditional customers through the table, the number of customers increases from 8476 to 10569. The average age is similar to the traditional group, which becomes a little larger (~46 for traditional group). The average of household median income of traditional customers is approximately 14,000 higher than the new customers. 

### Strengths and limitations
There are some limitations due to the methods that are used. Because of the large data, the generalized linear mixed model could not handle all variables at the same time. Thus, some variables that has small effects may not be included in the model.

\newpage
# Consultant information
## Consultant profiles

*Complete this section with a brief bio for each member of your group. If you are completing the project individually, you only need to complete one for yourself. In that case, change the title of this section to 'Consultant profile' instead. Examples below. This section is only marked for completeness, clarity and professionalism, not 'truth' so you can write it as if we're a few years in the future. Put your current degree in as completed and/or add your first choice grad school program, whatever you like. What skills related skills would you most like to highlight? What job title do you want?*

**Statsy McStatsstats**. Statsy is a senior consultant with Eminence Analytics. She specializes in data visualization. Statsy earned her Bachelor of Science, Specialist in Statistics Methods and Practice, from the University of Toronto in 2023.

**Datana Scatterplot**. Datana is a junior consultant with Eminence Analytics. They specialize in reproducible analysis and statistical communication. Datana earned their Bachelor of Science, Majoring in Computer Science and Statistics from the University of Toronto in 2024.

## Code of ethical conduct

_This section should be fairly short, no more than half a page. Assume a general audience, much like your executive summary._

* _Make at least three relevant statements about your company's approach to ethical statistical consulting. These should be appropriately in line with professional conduct advice like the (Statistical Society of Canada Code of Conduct)[https://ssc.ca/sites/default/files/data/Members/public/Accreditation/ethics_e.pdf] or the (Ethical Guidelines for Statistical Practice from the American Statistical Society)[https://www.amstat.org/ASA/Your-Career/Ethical-Guidelines-for-Statistical-Practice.aspx]. For example, "the customer is always right" ISN'T the type of thing an ethical statistical consultant would include._
*	_Be very careful not to just copy and paste from these other documents! Put things in your own words._


\newpage
# References

_You don't need to cite course materials, but consider all the the places you got data from, as well as the packages used and R itself. These are all things you should consider citing. Likewise, you might use some external resources on the emoji skin tones/Fitzpatrick scale, etc._

\newpage
# Appendix

_These appendices should outline in more detail the steps taken to access the following datasets. They should NOT include code, but should briefly describe the steps and important considerations. I.e., show that you understand what needs to be considered when web scraping, protecting licensed data, etc._

## Web scraping industry data on fitness tracker devices

## Accessing Census data on median household income

## Accessing postcode conversion files


__Final advice: KNIT EARLY AND OFTEN!__
